\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-06 paper/mswp2012-proposal.tex
extended WBS a little bit and removed unnecessary (s)

\begin{figure}[htb]
	\centering
		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
	\caption{User Centered Design Process TODO MATTHIAS QUELLE ANGEBEN!}
	\label{fig:UCD}
\end{figure}

@@

%\note{
%\begin{itemize}
%\item {\em Length: 2-4 pages}
%\item Structuring the project into self-contained parts.
%\item Additional verbal descriptions.
%\item Work packages
%    \begin{itemize}
%    \item title
%    \item goal(s)
%    \item description
%    \item expected results
%    \item responsible person(s)
%    \item dependencies
%    \end{itemize}
%\end{itemize}
%}

@@

\subsubsection{Literature Research LR1}
\label{sect:workplan:phase1:lr1}
\textbf{Dependencies:} None\\
\textbf{Description:} Find and describe existing systems and emphasis their approach.
Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
\textbf{Responsible person(s):} Research Group\\
\textbf{Goal(s) and expected Results:} Information about current systems, their feature set and user-interface\\

\subsubsection{Empirical Study ES1}
\label{sect:workplan:phase1:es1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}. They should evaluate these results and discover issues with their user-interface and functionality and also mention their needs regarding these two aspects.\\
The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
\textbf{Responsible person(s):} Research Group, Alpha-User \\
\textbf{Goal(s) and expected Results:} Knowledge about the user needs.\\

\subsubsection{Empirical Study ES2}
\label{sect:workplan:phase1:es2}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Meeting with possible service partners (restaruants, supermarkets, doctors, etc.) to identify their currently used systems and their needs, thoughts and whishes and specify how a cooperation could look like.\\
\textbf{Responsible person(s):} Strategy Team\\
\textbf{Goal(s) and expected Results:} Knowledge about the needs of service partners. Signed partner contracts. \\

\subsubsection{Range of Functions RF1}
\label{sect:workplan:phase1:rf1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Brainstorming about possible features of the system using knowledge discovered during step LR1 (\ref{sect:workplan:phase1:lr1}).\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Possible feature list\\

\pagebreak
\subsubsection{Range of Functions RF2}
\label{sect:workplan:phase1:rf2}
\textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the brainstormed feature list. Check if the discovered features from the empirical studies are matching the created feature list\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Final set of features for version 0.1 (Milestone M1)\\

@@

\subsubsection{Prototyping P1}
\label{sect:workplan:phase2:p1}
\textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered.\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} first version of prototype\\

\subsubsection{Evaluation and Redesign ER1}
\label{sect:workplan:phase2:er1}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and redesign it by taking care of their input. This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
\textbf{Responsible person(s):} Research Group, Alpha-Users, Dev Team\\
\textbf{Goal(s) and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\

\subsubsection{Prototyping P2}
\label{sect:workplan:phase2:p2}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} Extend the existing prototype by adding functionality and implement the features.\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} Prototype with all features\\

\pagebreak
\subsubsection{Evaluierung und Redesign ER2}
\label{sect:workplan:phase2:er2}
\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er2}\\
\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev Team (including Security and Quality Specialists). This step covers not only the interface and interaction, but also the quality and security of the product. The knowledge should be used to redesign the prototype and this step should be repeated several times. After a number of iterations the status of the web application should be switched to Beta and Beta-Users will be able to sign in and use the systems. After the last iteration the status should be switched to Release.\\
\textbf{Responsible person(s):} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
\textbf{Goal(s) and expected Results:} Released web application (Milestone M3)\\

@@

\subsubsection{Literature Research LR2}
\label{sect:workplan:phase3:lr2}
\textbf{Dependencies:} None\\
\textbf{Description:} Collect Knowledge about ubiquitous systems and figure out, how the product can be transformed into such a system by providing apps for smartphones. Search for techniques using NFC, GPS, WiFi, etc.\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Knowledge about ubiquitous systems and mobile apps\\

\subsubsection{Empirical Studie ES3}
\label{sect:workplan:phase3:es3}
\textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} User needs regarding an mobile app\\

\subsubsection{Range of Function RF2}
\label{sect:workplan:phase3:rf2}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Convert the knowledge from ES3 to a feature list and requirements for an mobile application.\\
\textbf{Responsible person(s):} Research Team\\
\textbf{Goal(s) and expected Results:} Feature list, requirements and interaction concept for an mobile app\\

\subsubsection{Prototyping P3}
\label{sect:workplan:phase3:p3}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Implement mobile version of the system with prototyping\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} Mobile clients\\

\subsubsection{Empirical Studie ES4}
\label{sect:workplan:phase3:es4}
\textbf{Dependencies:} None\\
\textbf{Description:} Establish if and which social health communities (e.g. tracking platforms) our users are using and find out how to integrate these partner into the system. \\
\textbf{Responsible person(s):} Research Team, Users\\
\textbf{Goal(s) and expected Results:} Possible new partners (3rd party services)\\

\subsubsection{Range of Function RF3}
\label{sect:workplan:phase3:rf3}
\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
\textbf{Description:} Use information gained from ES4 to specify 3rd party services to integrate into the system e.g. by finding APIs etc.\\
\textbf{Responsible person(s):} Research Team, Dev Team\\
\textbf{Goal(s) and expected Results:} Features (services to integrate)\\

\subsubsection{Prototyping P4}
\label{sect:workplan:phase3:p4}
\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
\textbf{Description:} Integrate established services into the system\\
\textbf{Responsible person(s):} Dev Team\\
\textbf{Goal(s) and expected Results:} System with integrated services\\

\subsubsection{Evaluierung und Redesign ER3}
\label{sect:workplan:phase3:er3}
\textbf{Dependencies:} P3 \ref{sect:workplan:phase3:p3}, P4 \ref{sect:workplan:phase3:p4}\\
\textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
\textbf{Responsible person(s):} Dev Team, Users\\
\textbf{Goal(s) and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\

>>>>

\begin{figure}[htb]
	\centering
		\includegraphics[width=0.8\textwidth]{images/method/UCD.pdf}
	\caption{User Centered Design Process [\cite{usability11}]}
	\label{fig:UCD}
\end{figure}

@@

%\note{
%\begin{itemize}
%\item {\em Length: 2-4 pages}
%\item Structuring the project into self-contained parts.
%\item Additional verbal descriptions.
%\item Work packages
%    \begin{itemize}
%    \item title
%    \item Goals
%    \item description
%    \item expected results
%    \item responsible persons
%    \item dependencies
%    \end{itemize}
%\end{itemize}
%}

@@

\subsubsection{Literature Research LR1}
\label{sect:workplan:phase1:lr1}
\textbf{Dependencies:} None\\
\textbf{Description:} Find and describe existing systems and emphasis their approach.
Analyze the user-interfaces and the provided interaction with the system. Establish the functionality and their business model.\\
\textbf{Responsible persons:} Research Group\\
\textbf{Goals and expected Results:} Information about current systems, their feature set and user-interface\\

\subsubsection{Empirical Study ES1}
\label{sect:workplan:phase1:es1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Create questionary for users, to get information about their thoughts about the systems discovered in \ref{sect:workplan:phase1:lr1}. They should evaluate these results and discover issues with their user-interface and functionality and also mention their needs regarding these two aspects.\\
The users current situation regarding the usage or the willingness to use of current systems are also parts to work out. \\
\textbf{Responsible persons:} Research Group, Alpha-User \\
\textbf{Goals and expected Results:} Knowledge about the user needs.\\

\subsubsection{Empirical Study ES2}
\label{sect:workplan:phase1:es2}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Meeting with possible service partners (restaruants, supermarkets, doctors, etc.) to identify their currently used systems and their needs, thoughts and whishes and specify how a cooperation could look like.\\
\textbf{Responsible persons:} Strategy Team\\
\textbf{Goals and expected Results:} Knowledge about the needs of service partners. Signed partner contracts. \\

\subsubsection{Range of Functions RF1}
\label{sect:workplan:phase1:rf1}
\textbf{Dependencies:} LR1 \ref{sect:workplan:phase1:lr1}\\
\textbf{Description:} Evaluating and complete feature set using knowledge discovered during step LR1 (\ref{sect:workplan:phase1:lr1}).\\
\textbf{Responsible persons:} Research Team\\
\textbf{Goals and expected Results:} Next draft of  feature list\\

\pagebreak
\subsubsection{Range of Functions RF2}
\label{sect:workplan:phase1:rf2}
\textbf{Dependencies:} RF1 \ref{sect:workplan:phase1:rf1}, ES1 \ref{sect:workplan:phase1:es1}, ES2 \ref{sect:workplan:phase1:es2}\\
\textbf{Description:} Combine knowledge from the two empirical studies ES1 and ES2 and evaluate the provisory feature list. Check if the discovered features from the empirical studies are matching the created feature list. Which features are really necessary and have an actual benefit for the users and stackholders? Which features are just nice to have or unnecessary at all?\\
\textbf{Responsible persons:} Research Team\\
\textbf{Goals and expected Results:} Final set of features for version 0.1 (Milestone M1)\\

@@

\subsubsection{Prototyping P1}
\label{sect:workplan:phase2:p1}
\textbf{Dependencies:} RF2 \ref{sect:workplan:phase1:rf2}\\
\textbf{Description:} Create first version of horizontal prototype by creating the user-interface. Every part of the system should be covered to make an evaluation of this prototype by a group of Alpha-Users possible. The users should get an idea how to use the product and experience the interaction.\\
\textbf{Responsible persons:} Dev Team\\
\textbf{Goals and expected Results:} first version of prototype\\

\subsubsection{Evaluation and Redesign ER1}
\label{sect:workplan:phase2:er1}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} The Alpha-Users should evaluate the prototype (interface and interaction) and the Dev-Team should redesign it by taking care of their input. This step should be repeated several times until there is no more additional useful feedback from the user-group.\\
\textbf{Responsible persons:} Research Group, Alpha-Users, Dev Team\\
\textbf{Goals and expected Results:} Information about necessary changes and redesigned prototype (Version 0.5, Milestone M2)\\

\subsubsection{Prototyping P2}
\label{sect:workplan:phase2:p2}
\textbf{Dependencies:} P1 \ref{sect:workplan:phase2:p1}\\
\textbf{Description:} Extend the existing prototype by adding functionality and implement the features. The prototype should extend the first version to create and get real data and not only stubs.\\
\textbf{Responsible persons:} Dev Team\\
\textbf{Goals and expected Results:} Prototype with all features as a base for the next evaluation step and the first release.\\

\pagebreak
\subsubsection{Evaluierung und Redesign ER2}
\label{sect:workplan:phase2:er2}
\textbf{Dependencies:} P2 \ref{sect:workplan:phase2:p2}, ER2 \ref{sect:workplan:phase2:er1}\\
\textbf{Description:} The new prototype should be reevaluated by the Alpha-Users and also from the Dev Team (including Security and Quality Specialists). This step covers not only the interface and interaction, but also the quality and security of the product. The knowledge should be used to redesign the prototype and this step should be repeated several times. After a number of iterations the status of the web application should be switched to Beta and Beta-Users will be able to sign in and use the systems. After the last iteration the status should be switched to Release.\\
\textbf{Responsible persons:} Alpha-Users, Beta-Users, Strategy Team, Dev Team\\
\textbf{Goals and expected Results:} Released web application (Milestone M3)\\

@@

\subsubsection{Literature Research LR2}
\label{sect:workplan:phase3:lr2}
\textbf{Dependencies:} None\\
\textbf{Description:} Collect Knowledge about ubiquitous systems and figure out, how the product can be transformed into such a system by providing apps for smartphones. Search for techniques using NFC, GPS, WiFi, etc. Investigate research topics using these techniques like localization, payment, and so on.\\
\textbf{Responsible persons:} Research Team\\
\textbf{Goals and expected Results:} Knowledge about ubiquitous systems and mobile apps\\

\subsubsection{Empirical Studie ES3}
\label{sect:workplan:phase3:es3}
\textbf{Dependencies:} LR2 \ref{sect:workplan:phase3:lr2}\\
\textbf{Description:} Establish user needs regarding an mobile app and get information about expectations of such an app. Find out how the user would use such an app and how this app would influence his daily life. Find ways to embedd this application in the users daily workflow and figure out, how the users could gain more benefits out of the product by providing such an mobile application.\\
\textbf{Responsible persons:} Research Team, Users\\
\textbf{Goals and expected Results:} User needs regarding an mobile app\\

\subsubsection{Range of Function RF2}
\label{sect:workplan:phase3:rf2}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Convert the knowledge from ES3 to a feature list and requirements for an mobile application.\\
\textbf{Responsible persons:} Research Team\\
\textbf{Goals and expected Results:} Feature list, requirements and interaction concept for an mobile app\\

\pagebreak
\subsubsection{Prototyping P3}
\label{sect:workplan:phase3:p3}
\textbf{Dependencies:} ES3 \ref{sect:workplan:phase3:es3}\\
\textbf{Description:} Implement mobile version of the system with prototyping. Features should include localization of the user to know, if the user is accessing establishment of service partner (e.g. restaurant, fitness center, etc.) and simple tracking of the users activities through NFC, QR-Code-Reader, etc.\\
\textbf{Responsible persons:} Dev Team\\
\textbf{Goals and expected Results:} Mobile clients\\

\subsubsection{Empirical Studie ES4}
\label{sect:workplan:phase3:es4}
\textbf{Dependencies:} None\\
\textbf{Description:} Establish if and which social health communities (e.g. tracking platforms) our users are using and find out how to integrate these partner into the system. \\
\textbf{Responsible persons:} Research Team, Users\\
\textbf{Goals and expected Results:} Possible new partners (3rd party services)\\

\subsubsection{Range of Function RF3}
\label{sect:workplan:phase3:rf3}
\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
\textbf{Description:} Use information gained from ES4 to specify 3rd party services to integrate into the system e.g. by finding APIs etc. It should be possible to e.g. include your sport activities from sport communities by using their API.\\
\textbf{Responsible persons:} Research Team, Dev Team\\
\textbf{Goals and expected Results:} Features (services to integrate)\\

\subsubsection{Prototyping P4}
\label{sect:workplan:phase3:p4}
\textbf{Dependencies:} ES4 \ref{sect:workplan:phase3:es4}\\
\textbf{Description:} Integrate established services into the system and create nice and intuitive interface to access these informations.\\
\textbf{Responsible persons:} Dev Team\\
\textbf{Goals and expected Results:} System with integrated services\\

\subsubsection{Evaluierung und Redesign ER3}
\label{sect:workplan:phase3:er3}
\textbf{Dependencies:} P3 \ref{sect:workplan:phase3:p3}, P4 \ref{sect:workplan:phase3:p4}\\
\textbf{Description:} Evaluate and redesign the system and mobile clients by the users with several iterations.\\
\textbf{Responsible persons:} Dev Team, Users\\
\textbf{Goals and expected Results:} Redesigned system and mobile clients (Version 1.0, Milestone M4)\\
